---
title: "TxRegInfra: support for TxRegQuery"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{TxRegInfra -- classes and methods for TxRegQuery}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes 
    theme: united
    toc: yes 
---

```{r setup,echo=FALSE,results="hide", eval=TRUE}
suppressPackageStartupMessages({
library(TxRegInfra)
library(GenomicFiles)
})
```

# Introduction

TxRegQuery addresses exploration of transcriptional regulatory networks
by integrating data on eQTL, digital genomic footprinting (DGF), DnaseI
hypersensitivity binding data (DHS), and transcription
factor binding site (TFBS) data.  Owing to the volume of emerging tissue-specific
data, special data modalities are used.

# Managing bed file content with mongodb

## Querying the `txregnet` database

We have a long-running server that will respond to queries.
We focus on `r CRANpkg("mongolite")` as the interface.

### The connection 

```{r lkmong, eval=TRUE}
suppressPackageStartupMessages({
library(TxRegInfra)
library(mongolite)
library(Gviz)
library(EnsDb.Hsapiens.v75)
library(BiocParallel)
register(SerialParam())
})
con1 = mongo(url=URL_txregInAWS(), db="txregnet")
con1
```
We will write methods that work with the 'fields' of this object.

There is not much explicit reflectance in the mongolite API.
The following is improvised and may be fragile:
```{r lkpar, eval=TRUE}
parent.env(con1)$orig
```

### Queries and aggregation

If the `mongo`
utility is available as a system
command, we can get a list of collections in the database
as follows.
```{r getl, eval=TRUE}
if (verifyHasMongoCmd()) {
  head(c1 <- listAllCollections(url=URL_txregInAWS(), db="txregnet"))
  }
```
Otherwise, as long as `r CRANpkg("mongolite")` is installed,
as long as we know the collection names of interest, we
can use them as noted throughout this vignette.

We can get a record from a given collection:
```{r getl2, eval=TRUE}
mongo(url=URL_txregInAWS(), db="txregnet", 
   collection="Adipose_Subcutaneous_allpairs_v7_eQTL")$find(limit=1)
```
Queries can be composed using JSON.  We have a tool
to generate queries that employ the mongodb aggregation
method.  Here we demonstrate this by computing, for each
chromosome, the count and
minimum values of the footprint statistic on CD14 cells.

```{r doagg, eval=TRUE}
m1 = mongo(url = URL_txregInAWS(), db = "txregnet",  collection="CD14_DS17215_hg19_FP")
newagg = makeAggregator( by="chr", vbl="stat", op="$min", opname="min")
```
The JSON layout of this aggregating query is
```
[
  {
    "$group": {
      "_id": ["$chr"],
      "count": {
        "$sum": [1]
      },
      "min": {
        "$min": ["$stat"]
      }
    }
  }
] 
```
Invocation returns a data frame:
```{r lkagggg, eval=TRUE}
head(m1$aggregate(newagg))
```


# An integrative container

We need to bind the metadata and information about the mongodb.

## Sample metadata

The following turns a very ad hoc filtering of the collection names
into a DataFrame.

```{r getcold, eval=TRUE}
# cd = makeColData() # works when mongo does
cd = TxRegInfra::basicColData
head(cd,2)
```

## Extended RaggedExperiment

```{r domor1, eval=TRUE}
rme0 = RaggedMongoExpt(con1, colData=cd)
rme1 = rme0[, which(cd$type=="FP")]
```

A key method in development is subsetting the archive by genomic coordinates.

```{r lksb, cache=TRUE, eval=TRUE}
s1 = sbov(rme1, GRanges("chr17", IRanges(38.07e6,38.09e6)))
s1
dim(sa <- sparseAssay(s1, 3))  # compact gives segfault
sa[953:956,c("fLung_DS14724_hg19_FP", "fMuscle_arm_DS17765_hg19_FP")]
```

# Visualizing coincidence

```{r mym, eval=TRUE}
ormm = txmodels("ORMDL3", plot=FALSE, name="ORMDL3")
sar = strsplit(rownames(sa), ":|-")
an = as.numeric
gr = GRanges(ormm@chromosome, IRanges(an(sapply(sar,"[", 2)), an(sapply(sar,"[", 3))))
gr1 = gr
gr1$score = 1-sa[,1]
gr2 = gr
gr2$score = 1-sa[,2]
sc1 = DataTrack(gr1, name="Lung FP")
sc2 = DataTrack(gr2, name="Musc/Arm FP")
plotTracks(list(GenomeAxisTrack(), sc1, sc2, ormm), showId=TRUE)
```




