---
title: "TxRegInfra: support for TxRegQuery"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{TxRegInfra -- classes and methods for TxRegQuery}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::pdf_document:
    toc: yes 
    number_sections: yes 
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes 
    theme: united
    toc: yes 
---

```{r setup,echo=FALSE,results="hide"}
suppressPackageStartupMessages({
library(TxRegInfra)
library(GenomicFiles)
library(RMongo)
})
```

# Introduction

TxRegQuery addresses exploration of transcriptional regulatory networks
by integrating data on eQTL, digital genomic footprinting (DGF), DnaseI
hypersensitivity binding data (DHS), and transcription
factor binding site (TFBS) data.  Owing to the volume of emerging tissue-specific
data, special data modalities are used.

# Managing bed file content with mongodb

## Importing and querying documents

The package comes with a small number of bed files to demonstrate
import utilities.
```{r lkk}
# ENCODE
f1 = dir(system.file("bedfiles", package="TxRegInfra"), full=TRUE, patt="ENCFF971VCD")
cat(readLines(f1, n=3), sep="\n")
# ChromHMM
f2 = dir(system.file("bedfiles", package="TxRegInfra"), full=TRUE, patt="E096_imp12")
cat(readLines(f2, n=3), sep="\n")
```

There is a `bedType` parameter that indicates what fields are available; it
defaults to `broadPeak`.

The following code imports a broadPeak and chromHMM document.
We deal with metadata about these documents below.
We assume a database called 'txregnet' has been established
for a running mongodb server.
```{r doimp}
importBedToMongo(f1, "vjc1", db="txregnet")
importBedToMongo(f2, "vjc2", db="txregnet", bedType="chromHMM")
```

Now that the documents are imported, we can query for
information in an interval specified by a GRanges instance.
```{r doq}
library(RMongo)
con = mongoDbConnect("txregnet") # defaults for local server
queryBedInMongo(con, "vjc1", GRanges("chr1", IRanges(1, 800000)), skip=0, limit=5)
queryBedInMongo(con, "vjc2", GRanges("chr17", IRanges(1, 800000)), skip=0, limit=5)
```

# An integrative container

We need to bind the metadata and information about the mongodb.

## BED file metadata

The BED files are extracted from a few different places.  We have
metadata on 10 of them:
```{r lkmeta}
data(hsFiles)
hsFiles[1:3,1:6]
```
We added an additional four.  This will become colData for an
instance of an extended RaggedExperiment class to be defined.
```{r donew,echo=FALSE}
library(S4Vectors)
e072 = data.frame(File.accession = "E072_imp12_mn_trun",
   File.format = "bed ChromHMM", Output.type = "states", Experiment.accession=NA,
    Assay = "ChromHMM", Biosample.term.id=NA, 
    Biosample.term.name="brain inf. temporal lobe",
    Biosample.type=NA,
    Biosample.life.stage=NA, Biosample.sex=NA)
e073 = data.frame(File.accession = "E073_imp12_mn_trun",
   File.format = "bed ChromHMM", Output.type = "states", Experiment.accession=NA,
    Assay = "ChromHMM", Biosample.term.id=NA, 
    Biosample.term.name="brain prefr. cortex",
    Biosample.type=NA,
    Biosample.life.stage=NA, Biosample.sex=NA)
e088 = data.frame(File.accession = "E088_imp12_mn_trun",
   File.format = "bed ChromHMM", Output.type = "states", Experiment.accession=NA,
    Assay = "ChromHMM", Biosample.term.id=NA, 
    Biosample.term.name="fetal lung",
    Biosample.type=NA,
    Biosample.life.stage=NA, Biosample.sex=NA)
e096 = data.frame(File.accession = "E096_imp12_mn_trun",
   File.format = "bed ChromHMM", Output.type = "states", Experiment.accession=NA,
    Assay = "ChromHMM", Biosample.term.id=NA, 
    Biosample.term.name="adult lung",
    Biosample.type=NA,
    Biosample.life.stage=NA, Biosample.sex=NA)
```
```{r lkcd}
cd = DataFrame(rbind(hsFiles, rbind(e072, e073, e088, e096)))
cd[1:4,1:6]
```

## Extended RaggedExperiment

```
library(RaggedExperiment)
setClass("RaggedMongoExpt", contains="RaggedExperiment",
    representation=representation(dbName="character"))
```


## Cleanup

In a multiuser system this could cause problems if someone
is running examples or building vignette.  May need to
use munged collection names, perhaps with uuids.

```{r doclean}
try(system('mongo txregnet --eval "db.vjc1.remove({})"'))
try(system('mongo txregnet --eval "db.vjc2.remove({})"'))
```





