---
title: "txRegInfOb"
author: Vince Carey, BJ Stubbs, Shweta Gopaulakrishnan
date: November 2017
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
---

# Introduction

This is a tech demo of how we can create an object structure for txRegQuery

# Level 1

The primitive is a list containing information about the txRegQuery object

The goal here is to package the data connection details in the resAdapter slot and the resource metadata in the resMeta slot.

For an example, we will use the hsFiles data frame which is a subset of the metadata for the DNAse HS data resources.


```{r lev1}
setClass(
  Class="txInfraSource",
  representation=representation(
    resName="character",
    resType="character",
    resOrigin="character",
    resAdapter="list",
    resMeta="list"
  )
)

load("hsFiles.rda")
hsFiles

mylist=lapply(1:nrow(hsFiles),
  function(i){
    new(Class="txInfraSource",
      resName=hsFiles[i,"File.accession"],
      resType=hsFiles[i,"Output.type"],
      resOrigin=hsFiles[i,"Experiment.accession"],
      resAdapter=list(type="mongo",
        location="txregnet",host="localhost",
        chrCol="chrom",
        startCol="chromStart",
        endCol="chromEnd",
        chrSeqStyle="ucsc",
        suffix="_hg19_HS"
        ),
      resMeta=hsFiles[i,]
  )
 }
)

```

# Level 2

The class txInfraColl is a collection of txInfraSources

```{r lev2}
setClass("txInfraColl",
  representation(collection="list"
  )
)

myColl=new(Class="txInfraColl",collection=mylist)
```

# Methods 1 - Show

Show methods

```{r methods1}
setMethod("show", "txInfraSource", function(object) {
  cat("txInfra Resource Instance for", object@resName,
    "of type", object@resAdapter[["type"]],"\n")
})

setMethod("show", "txInfraColl", function(object) {
  cat("txInfra Resource Collection with", length(object@collection),
    "Resources","\n")
})

myColl

myColl@collection[[1]]
```

# Methods 2 - Query

```{r methods2 }

setMethod("head", "txInfraSource", function(x) {
  require(RMongo)
  my_collection = paste0(x@resName,x@resAdapter[["suffix"]])
  db = x@resAdapter[["location"]]
  mongo <- mongoDbConnect(db, "localhost", 27017)
  output <- RMongo::dbGetQuery(mongo, my_collection,'{}',0,7)
  print(output)
  RMongo::dbDisconnect(mongo)
  rm(mongo)
})

head(myColl@collection[[1]])

txRegRangeQuery<-function(myTxSource, mychr, mystart,myend){
  require(RMongo)
  require(rjson)
  if(myTxSource@resAdapter[["type"]]=="mongo"){
    my_collection = paste0(myTxSource@resName,myTxSource@resAdapter[["suffix"]])
    db = myTxSource@resAdapter[["location"]]
    mongo <- mongoDbConnect(db, "localhost", 27017)
    myChrCol=myTxSource@resAdapter[["chrCol"]]
    myStartCol=myTxSource@resAdapter[["startCol"]]
    myEndCol=myTxSource@resAdapter[["endCol"]]
    if(myTxSource@resAdapter[["chrSeqStyle"]]=="ucsc"){mychr=paste0("chr",mychr)}
    mylist=list()
    mylist[[myChrCol]]=mychr;
    if(myStartCol==myEndCol){
      mylist[[myStartCol]]=list("$gte"=mystart,"$lte"=myend)
    }else{
        mylist[[myStartCol]]=list("$gte"=mystart)
        mylist[[myEndCol]]=list("$lte"=myend)
    }
    myquery=toJSON(mylist)
    output <- RMongo::dbGetQuery(mongo, my_collection,myquery)
    RMongo::dbDisconnect(mongo)
    rm(mongo)
    return(output)
  }else{cat("Rest not done yet")}
}

txRegRangeQuery(myColl@collection[[1]], 1, 713840, 763840)
```


# Ragged Experiment

We can construct a RaggedExperiment using the query results and meta data

```{r ragged}
require(RaggedExperiment)
library(erma)

#set up window for query
mygene=genemodel("ORMDL3")
window=50000
mystart=min(start(mygene))-window
myend=max(end(mygene))+window

#run queries
myGList=lapply(1:5, function(x){
  myChrCol=myColl@collection[[x]]@resAdapter[["chrCol"]]
  myStartCol=myColl@collection[[x]]@resAdapter[["startCol"]]
  myEndCol=myColl@collection[[x]]@resAdapter[["endCol"]]
  res=txRegRangeQuery(myColl@collection[[x]], 17, mystart, myend)
  GRanges(res[[myChrCol]], IRanges(res[[myStartCol]], res[[myEndCol]]), mcols=res)
})

#harmonize mcols
myvars=unique(unlist(lapply(myGList,function(x){names(mcols(x))})))
for(i in 1:length(myGList)){
  diffvars=setdiff(myvars,names(mcols(myGList[[i]])))
  if(length(diffvars)>0){mcols(myGList[[i]])[,diffvars]=NA}
  mcols(myGList[[i]])=mcols(myGList[[i]])[,myvars]
}

myColData=do.call(rbind.data.frame,lapply(1:5, function(x){myColl@collection[[x]]@resMeta}))
row.names(myColData)=myColData[,1]
myRagged=RaggedExperiment(myGList, colData=myColData)
myRagged

```

# Functionalize

```{r func}
txRagged<-function(mychr,mystart,myend,mycoll){
  myGList=lapply(mycoll@collection, function(x){
    myChrCol=x@resAdapter[["chrCol"]]
    myStartCol=x@resAdapter[["startCol"]]
    myEndCol=x@resAdapter[["endCol"]]
    res=txRegRangeQuery(x, mychr, mystart, myend)
    GRanges(res[[myChrCol]], IRanges(res[[myStartCol]], res[[myEndCol]]), mcols=res)
  })

  #harmonize mcols
  myvars=unique(unlist(lapply(myGList,function(x){names(mcols(x))})))
  for(i in 1:length(myGList)){
    diffvars=setdiff(myvars,names(mcols(myGList[[i]])))
    if(length(diffvars)>0){mcols(myGList[[i]])[,diffvars]=NA}
    mcols(myGList[[i]])=mcols(myGList[[i]])[,myvars]
  }

  myColData=do.call(rbind.data.frame,lapply(mycoll@collection, function(x){x@resMeta}))
  row.names(myColData)=myColData[,1]
  myRagged=RaggedExperiment(myGList, colData=myColData)
  myRagged
}

myColl
myRagged2=txRagged(17,mystart,myend, myColl)
myRagged2
```

# Extension to eQTL data

We can use this framework with the eQTL data as well.

```{r eQTL}
wbEQTL=new(Class="txInfraSource",
  resName="Whole_Blood_Analysis_v6p_all_snpgene_pairs_eQTL",
  resType="GTEx eQTL",
  resOrigin="GTEx version 6",
  resAdapter=list(type="mongo",
    location="txregnet",host="localhost",
    chrCol="snp_chr",
    startCol="snp_pos",
    endCol="snp_pos",
    chrSeqStyle="NCBI",
    suffix=""
    ),
  resMeta=list()
)

txRegRangeQuery(wbEQTL, 17, mystart, myend)[1:5,]

```
